Adults 6-0-0/5-1-0 overview

### 2018-12-18 analysis/01_adult_it_overview.Rmd
update adult overview analysis file

```{r}
d510 %>%
  filter(phase != "training") %>%
  group_by(experiment, workerid) %>%
  summarise(correct = mean(correct_target1)) %>%
  summarise(correct = list(correct)) %>%
  group_by(experiment) %>%
  mutate(mu = bayes.t.test(unlist(correct), mu = 1/3)$stats[1,1],
         HDIlo = bayes.t.test(unlist(correct), mu = 1/3)$stats[1,5],
         HDIup = bayes.t.test(unlist(correct), mu = 1/3)$stats[1,6],
         eff.size = bayes.t.test(unlist(correct), mu = 1/3)$stats[4,1]) %>%
  select(mu,HDIlo,HDIup,eff.size)
```

>>>>

```{r}
d510 %>%
  filter(phase != "training",
         experiment == "recency_look") %>%
  group_by(experiment, workerid) %>%
  summarise(correct = mean(correct_target1)) %>%
  summarise(correct = list(correct)) %>%
  group_by(experiment) %>%
  mutate(mu = bayes.t.test(unlist(correct), mu = 1/3)$stats[1,1],
         HDIlo = bayes.t.test(unlist(correct), mu = 1/3)$stats[1,5],
         HDIup = bayes.t.test(unlist(correct), mu = 1/3)$stats[1,6],
         eff.size = bayes.t.test(unlist(correct), mu = 1/3)$stats[4,1]) %>%
  select(mu,HDIlo,HDIup,eff.size)
```
